### 2018-10-14 pkg/colorspace/index.Rmd
renamed hcl_palettes(name = ...) and divergingx_palettes(name = ...) to palette = ... for consistency with actual palette functions and ggplot2 scales
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@338 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r palettes, echo = FALSE, fig.show = "hide", fig.width = 4.5, fig.height = 4.5, fig.align = "center", dev = "png", dpi = 48}
hcl_palettes(name = c(
  "Pastel 1", "Dark 3", "Harmonic",
  "Blues 3", "Greens 3", "Reds 3",
  "Heat", "Purple-Blue", "Viridis",
  "Blue-Red", "Green-Brown", "Tropic"
), plot = TRUE, n = 7)
```

>>>>

```{r palettes, echo = FALSE, fig.show = "hide", fig.width = 4.5, fig.height = 4.5, fig.align = "center", dev = "png", dpi = 48}
hcl_palettes(palette = c(
  "Pastel 1", "Dark 3", "Harmonic",
  "Blues 3", "Greens 3", "Reds 3",
  "Heat", "Purple-Blue", "Viridis",
  "Blue-Red", "Green-Brown", "Tropic"
), plot = TRUE, n = 7)
```
